---
title: '02_BlockImputation_Incident_Table'
author: "Philip Lee"
date: "July 16, 2021"
output:
  html_document: default
  pdf_document: default
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(dbplyr)
library(tidyverse)
library(bit64) #Use for making the NAs for the large numbers created by a known bug in R
library(DT)
library(lubridate)
library(data.table)

set.seed(414425)
#KJ: read in in the main run program
read_csv <- partial(read_csv, guess_max = 100000) #For now, read thru the 1st 100,000 rows to determine variable type
write.csv <- partial(write.csv, na = "", row.names = FALSE)

```

<!-- ------------------------------------------------------------------------------- -->
<!--  Create the database connection. -->

```{r}

#Read in data from query that contains all the incidents in the provided year
df1 <- read_csv(file=paste0(queried_data_path, "incidents_population_groups_", CONST_YEAR, ".csv.gz"))

log_dim(df1)
head(df1)
glimpse(df1)



```

```{r}

#Read in the block imputed file
#raw_blockimp <- read_csv(paste0(outblockimp, "donorids.csv"))
raw_blockimp <- fread(paste0(inblockimp, "donorids.csv"))

log_dim(raw_blockimp)
glimpse(raw_blockimp)

#Need to transform the above data from wide to long
raw_blockimp2 <- raw_blockimp %>%
  gather(key="month", value="value", -ori, -ori.don) %>%
  #Filter to non-missing entries
  filter(!is.na(value)) %>%
  mutate(
    der_month = case_when(
      trim_upcase(month) == 'JAN' ~ 1,
      trim_upcase(month) == 'FEB' ~ 2,
      trim_upcase(month) == 'MAR' ~ 3,
      trim_upcase(month) == 'APR' ~ 4,
      trim_upcase(month) == 'MAY' ~ 5,
      trim_upcase(month) == 'JUN' ~ 6,
      trim_upcase(month) == 'JUL' ~ 7,
      trim_upcase(month) == 'AUG' ~ 8,
      trim_upcase(month) == 'SEP' ~ 9,
      trim_upcase(month) == 'OCT' ~ 10,
      trim_upcase(month) == 'NOV' ~ 11,
      trim_upcase(month) == 'DEC' ~ 12)
  )

log_dim(raw_blockimp)
log_dim(raw_blockimp2)
glimpse(raw_blockimp2)

#Check the recodes
raw_blockimp2 %>%
  checkfunction(der_month, month)

#Create the derived variable on df1
df1_2 <- df1 %>% 
  mutate(der_month = month(ymd(incident_date) ))

df1_2 %>%
  checkfunction(der_month, incident_date)

#df1_2 holds all the incident_id plus recodes

#Need to create the imputed block and call it df1_3
df1_3<- raw_blockimp2 %>%
  #Do a join using the donor ori and match with the incident month
  left_join(df1_2, by=c("ori.don"="ori", "der_month") ) %>%
  #Drop rows that have no incident_id 
  filter(!is.na(incident_id))

#NEW:  need to do the following on the raw data (i.e. df1_2)
#1:  Need to drop any incidents that are before the NIBRS start date
#2:  Need to drop any incidents that are missing (i.e. RETA MM flag = 0) or low outliers 

#Need to get list of ori and incident ids that are low outliers and missing months

df_raw_data1 <- df1_2 %>%
  left_join(raw_blockimp2, by=c("ori"="ori", "der_month"))

#Check to see if the number of records are the same
log_dim(df_raw_data1)
log_dim(df1_2)
log_dim(raw_blockimp2)

#Check to see which values are flagged
df_raw_data1 %>% checkfunction(value)

#Create flag to handle dropping of data
df_raw_data2 <- df_raw_data1 %>%
  mutate(
    der_drop_missing_month_low_outlier = fcase(value %in% c(1,2), 1, 
                                               default = 0),
    
    der_drop_inc_bf_nsd = fcase(incident_date < nibrs_start_date, 1,
                                               default = 0)
  )

#Check the recodes
df_raw_data2 %>% checkfunction(der_drop_missing_month_low_outlier, value)
df_raw_data2 %>% checkfunction(der_drop_inc_bf_nsd, nibrs_start_date, incident_date)
df_raw_data2 %>% checkfunction(der_drop_inc_bf_nsd)

#Next need to drop the flagged incidents
final_raw_data_keep <- df_raw_data2 %>%
  filter(der_drop_missing_month_low_outlier == 0 & der_drop_inc_bf_nsd == 0)

#Check the size
log_dim(final_raw_data_keep)
log_dim(df_raw_data2)

final_raw_data_keep %>% checkfunction(der_drop_missing_month_low_outlier, der_drop_inc_bf_nsd)


#Stack the original data final_raw_data_keep and block imputed data df1_3 together
final <- bind_rows(final_raw_data_keep %>% mutate(der_imputed_incident = 0), 
                   df1_3 %>% mutate(der_imputed_incident = 1))

log_dim(final)
log_dim(final_raw_data_keep)
log_dim(df1_3)

#See the number of records
final %>%
  checkfunction(der_imputed_incident)

#Keep selected variables for output
final2 <- final %>%
  select(ori, incident_id, der_imputed_incident)

#Check to see if there are any duplicate records for ori and incident_id combination
raw_check <- final2 %>%
  group_by(ori, incident_id) %>%
  summarise(raw_count = n() ) %>%
  ungroup() 
  
raw_check %>%
  checkfunction(raw_count)

final2 <- final2 %>% 
  filter(!is.na(ori)) %>%
  arrange(ori,incident_id)

#Output the dataset to the share
final2 %>% write.csv(gzfile(paste0(outblockimp, "NIBRS_INCIDENT_PLUS_IMPUTED_BLOCK.csv.gz")))


