---
title: '1 - Check imputation demographics'
author: "Philip Lee"
date: "June 14, 2022"
output:
  html_document: default
  pdf_document:  default
---

```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(tidyverse)
library(DT)
library(data.table)
```


```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}

#Create a function to gather the files

processfiles <- function(infilepath, intype){
  
  log_trace("In function processfiles")
  #Get all of the csv files
  raw_list_files <- list.files(path=input_item_imp, pattern=paste0("17_\\w+_", intype, "_imputed_final_flag_hisp.csv.gz"), full.names=TRUE)
  
  #Print the path
  log_trace("Printing the files that will be read in:")
  print(raw_list_files)
  
  #Create a list object to hold results
  raw_list_1 <- vector("list", length(raw_list_files))
  
  #Loop thru the list 
  for(i in 1:length(raw_list_1)){
    
    #Get the current path of the file
    raw_file <- raw_list_files[[i]]
    
    #Get the state
    raw_state <- str_match(raw_file, paste0("17_(\\w+)_", intype, "_imputed_final_flag_hisp.csv.gz")) %>%
      as_tibble() %>%
      select(2) %>%
      pull()
    
    #Save to a list
    raw_list_1[[i]] <- fread(file=raw_file)[, state := raw_state] %>% recode_all_ethnicity_ints_to_char()
    
  }
  
  #Return the list object
  return(raw_list_1 %>% rbindlist())
}

#Get the files
raw_victim <- processfiles(infilepath=input_item_imp, intype="victim") 
raw_arrestee <- processfiles(infilepath=input_item_imp, intype="arrestee")
raw_offender <- processfiles(infilepath=input_item_imp, intype="offender")

#Take a look at the dataset
glimpse(raw_victim)
glimpse(raw_arrestee)
glimpse(raw_offender)

#Create a function to summarise
summarize_demo <- function(indata, inraw, inimp, innewvar, inselect){
  log_trace("In function summarize_demo")
  
  #Create new symbol
  in2newvar <- innewvar %>% rlang:::parse_expr()
  
  #Process the variable - National
  tbd_1 <- indata %>%
    group_by(!!inraw) %>%
    summarise(raw_count = n()) %>%
    mutate(raw_percentage=roundfunction((raw_count/sum(raw_count)))) %>%
    rename(!!in2newvar := !!inraw) %>%
    mutate(state="National")
  
  tbd_2 <- indata %>%
    group_by(!!inimp) %>%
    summarise(imputed_count = n()) %>%
    mutate(imputed_percentage=roundfunction((imputed_count/sum(imputed_count))))  %>%
    rename(!!in2newvar := !!inimp) %>%
    mutate(state="National")
  
  #National only
  tbd_national <- tbd_1 %>%
    full_join(tbd_2, by=c("state", innewvar)) %>%
    select(state, !!in2newvar, !!!inselect)
  
  #Process the variable - state
  tbd_state_1 <- indata %>%
    group_by(state, !!inraw) %>%
    summarise(raw_count = n()) %>%
    mutate(raw_percentage=roundfunction((raw_count/sum(raw_count)))) %>%
    rename(!!in2newvar := !!inraw) 
  
  tbd_state_2 <- indata %>%
    group_by(state, !!inimp) %>%
    summarise(imputed_count = n()) %>%
    mutate(imputed_percentage=roundfunction((imputed_count/sum(imputed_count))))  %>%
    rename(!!in2newvar := !!inimp) 
  
  #State only
  tbd_state <- tbd_state_1 %>%
    full_join(tbd_state_2, by=c("state", innewvar))%>%
    select(state, !!in2newvar, !!!inselect)
  
  #Stack the results
  final <- bind_rows(tbd_national,tbd_state)
  
  #Return the final data
  return(final)

}


#Creating a function to compare the distributions
compareit <- function(intype){
  log_trace("In function compareit")
  #Declare the variable
  in_raw_ethnicity_code    = paste0("ethnicity_code_",intype,"_raw") %>% rlang:::parse_expr()
  in_imputed_ethnicity_code   = paste0("ethnicity_code_",intype,"_i") %>% rlang:::parse_expr()

  #Need to create distribution comparing the raw and imputed values 
  inselect = c("raw_count", "raw_percentage", "imputed_count", "imputed_percentage") %>% rlang:::parse_exprs()
  
  #Get the raw dataset
  raw0 <- get(paste0("raw_",intype))
  
  raw1 <-  raw0 %>%
    #select the variables of interest
    select( state,
            #Raw variables
            !!in_raw_ethnicity_code,
            #Imputed variables
            !!in_imputed_ethnicity_code) 
  
  #Process the ethnicity
  raw_ethnicity <- summarize_demo(indata=raw1, inraw=in_raw_ethnicity_code, inimp=in_imputed_ethnicity_code, innewvar="ethnicity_code", inselect=inselect) %>%
    #Create the recode
    mutate(ethnicity_label = fcase(
      ethnicity_code == "H", "Hispanic or Latino",
      ethnicity_code == "N", "Not Hispanic or Latino",
      ethnicity_code == "M", "Multiple",
      ethnicity_code == "U", "Missing"
  )) %>% select(
      state, ethnicity_label, ethnicity_code, !!!inselect)

  #Return the list of results
  return( list(raw_ethnicity) )

}

#Create a function to create the der_percentage_difference_outlier_mean variable

createoutliervar <- function(indata){
  log_trace("In function createoutliervar")
  #Create a list
  returndata <- vector("list", length(indata))
  
  for(i in 1:length(returndata)){
  
  returndata[[i]] <- indata[[i]]  %>%
    #Calculate the percentage difference variable
    mutate(der_percentage_difference = imputed_percentage - raw_percentage,
           one = 1) %>%
    #Group by one
    group_by(one) %>%
    mutate(der_percentage_difference_mean = mean(der_percentage_difference, na.rm=TRUE),
           der_percentage_difference_sd = sd(der_percentage_difference, na.rm=TRUE),
           der_percentage_difference_outlier_mean = fcase(
             
             #The upper bound
             der_percentage_difference_mean + 3*der_percentage_difference_sd < der_percentage_difference, 1,
             
             #The lower bound
             der_percentage_difference_mean - 3*der_percentage_difference_sd > der_percentage_difference, 1,
             default = 0
           )) %>%
    ungroup() %>%
    select(-one, -der_percentage_difference_mean, -der_percentage_difference_sd)
  }
  
  return(returndata)

}




#Call the function
final_victim   <- compareit(intype="victim") %>% createoutliervar()
final_arrestee <- compareit(intype="arrestee") %>% createoutliervar()
final_offender <- compareit(intype="offender") %>% createoutliervar()



#Create a format function
formatfunction <- function(indata, inlabel, incaptionstyle){
    log_trace("In function formatfunction")
    #Format the columns
    indata2 <- datatable(indata,
	            filter = "top", 
	            options = list(pageLength = 100, autoWidth = TRUE),
                caption = htmltools::tags$caption(
                    style = incaptionstyle,
                    inlabel)) %>%
                formatPercentage(c("raw_percentage", "imputed_percentage", "der_percentage_difference"), 2) %>%
                formatRound(c("raw_count", "imputed_count"), digits = 0)
    
    #Call the print
    htmltools:::tagList(indata2)
  
}


formatfunctionoutlier <- function(indata, inlabel, incaptionstyle){
    log_trace("In function formatfunctionoutlier")
    #Format the columns
    indata2 <- datatable(indata,
	            filter = "top", 
	            options = list(pageLength = 100, autoWidth = TRUE),
                caption = htmltools::tags$caption(
                    style = incaptionstyle,
                    inlabel)) %>%
                formatPercentage(c("raw_percentage", "imputed_percentage", "der_percentage_difference"), 2) %>%
                formatRound(c("raw_count", "imputed_count"), digits = 0) %>%
                #Add code to highlight outlier rows
                formatStyle("der_percentage_difference_outlier_mean",
                            target="row",
                            backgroundColor = styleEqual(1, "yellow"))
    
    #Call the print
    htmltools:::tagList(indata2)
  
}


#Create caption font
incaptionstyle = 'caption-side: top; text-align: center; font-size: 75px'

#Create a function to subset to outlier states 
subsetoutlierstate <- function(indata){
  log_trace("In function subsetoutlierstate")
  returndata <- indata %>%
                 #Group by state to detect any outliers
                 group_by(state) %>%
                 mutate(der_any_mean_outlier = any(der_percentage_difference_outlier_mean == 1)) %>%
                 ungroup() %>%
                 #Filter to impacted records
                 filter(der_any_mean_outlier == 1) %>%
                 select(-der_any_mean_outlier)
} 

```
This is the validation report for the victim, arrestee, and offender segments for the hispanic variables. 

Below are the tables that show the distribution of the raw data (i.e. columns raw_count and raw_percentage) and after imputation (i.e. columns imputed_count and imputed_percentage) for the victim, offender, and arrestee segments for the hispanic variable.  Each table shows the distribution at the national level and broken down by the 50 states plus DC.

Please note for the arrestee and offender segments, imputation is done on cleared incidents only (i.e. there is an arrestee in an incident or the incident is cleared exceptionally) and for eligible NIBRS agencies.

For the victim segment, all victims in eligible NIBRS agencies are imputed and includes both cleared and uncleared incidents.  

In the columns, raw_count and raw_percentage, there are missing or unknown values and they are removed in the imputed columns (i.e. imputed counts and imputed_percentage). 

The percentages are within National or each of the 50 states plus D.C.

* Note the tables with "Outlier" in the title, flags any outliers on the column, der_percentage_difference.
    + Differences that are more than 3 standard deviations away from the mean difference are flagged as outliers.
    + For the purpose of these tables, all rows from the impacted domain (i.e. column state is shown) and any rows detected as an outlier is highlighted.  
    + The mean and standard deviations used comes from der_percentage_difference and is calculated within each of the tables (i.e. Victim Hispanic and same for Arrestee and Offender).  



```{r, echo=FALSE, message=FALSE}

##############################################Victim table###################################################
formatfunction(       indata=final_victim[[1]],                          inlabel = 'Victim Ethnicity Table',         incaptionstyle=incaptionstyle)
formatfunctionoutlier(indata=final_victim[[1]] %>% subsetoutlierstate(), inlabel = 'Victim Ethnicity Outlier Table', incaptionstyle=incaptionstyle)


##############################################Arrestee table###################################################
formatfunction(       indata=final_arrestee[[1]],                          inlabel = 'Arrestee Ethnicity Table',         incaptionstyle=incaptionstyle)
formatfunctionoutlier(indata=final_arrestee[[1]] %>% subsetoutlierstate(), inlabel = 'Arrestee Ethnicity Outlier Table', incaptionstyle=incaptionstyle)


##############################################Offender table###################################################
formatfunction(       indata=final_offender[[1]],                          inlabel = 'Offender Ethnicity Table',         incaptionstyle=incaptionstyle)
formatfunctionoutlier(indata=final_offender[[1]] %>% subsetoutlierstate(), inlabel = 'Offender Ethnicity Outlier Table', incaptionstyle=incaptionstyle)



```

```{r, echo=FALSE, message=FALSE}

##############################################Victim table###################################################
formatfunction(indata=final_victim[[1]] %>% filter(is.na(ethnicity_code) & !is.na(imputed_count)) , inlabel = 'Any Unknown/Missing Victim Ethnicity After Imputation Table', incaptionstyle=incaptionstyle)

##############################################Arrestee table###################################################
formatfunction(indata=final_arrestee[[1]] %>% filter(is.na(ethnicity_code) & !is.na(imputed_count)), inlabel = 'Any Unknown/Missing Arrestee Ethnicity After Imputation Table', incaptionstyle=incaptionstyle)


##############################################Offender table###################################################
formatfunction(indata=final_offender[[1]] %>% filter(is.na(ethnicity_code) & !is.na(imputed_count)), inlabel = 'Any Unknown/Missing Offender Ethnicity After Imputation Table', incaptionstyle=incaptionstyle)




```

